\vspace{-1cm} Model linearity breeds contempt: using Bayesian non-linear models to uncover broad macroecological patterns

### 2021-06-22 manuscript/manuscript.tex
baseline model 2d

\section*{Results}
We studied the distribution data to characterize species' realized niches along the main axis of variation of all environmental variables. Using the presence and absence of species across sites as the response variable, we sampled the posterior distributions of the baseline model, accounting for the information in the floristic database regarding species' indicator values and range of variation. This allowed us to map the center and variance of species' distributions along the environmental gradient (Fig.~\ref{fig:correlation}).  Studying the relationship between these properties, we found these to be negatively correlated (i.e.~$\beta_{i}$ and $\gamma_{i}$ in the baseline model were positively correlated; Fig.~\ref{fig:correlation}). This means that species found at lower elevations have generally wider distributions than those at higher elevations. The same relationship was found when using instead elevation or mean temperature as explanatory variables (Supplementary Fig.~XX) as well as when using ordinal data (Supplementary Fig.~XX); however, the pattern was not present along the second main axis of variation of our environmental variables (Supplementary Fig.~XX). The comparison between the other parameter estimates revealed additional, somewhat more expected, relationships. In particular, we found the amplitude of distributions to be positively and negatively correlated with their mean and variance, respectively (i.e. $\alpha_{i}$ is positively correlated with $\beta_{i}$ and $\gamma_{i}$; Supplementary Fig.~XX). This implies that, at higher elevations, species' distributions generally have lower amplitudes.

>>>>

\section*{Results}
We studied the distribution data to characterize species' realized niches along the main axis of variation of all environmental variables. Using the presence and absence of species across sites as the response variable, we sampled the posterior distributions of the baseline model, accounting for the information in the floristic database regarding species' indicator values and range of variation. This allowed us to map the center and variance of species' distributions along the environmental gradient (Fig.~\ref{fig:correlation}).  Studying the relationship between these properties, we found these to be negatively correlated (i.e.~$\beta_{i}$ and $\gamma_{i}$ in the baseline model were positively correlated; Fig.~\ref{fig:correlation}). This means that species found at lower elevations have generally wider distributions than those at higher elevations. The same relationship was found when using instead elevation or mean temperature as explanatory variables (Supplementary Fig.~3) as well as when using ordinal data (Supplementary Fig.~4); however, the pattern was not present along the second main axis of variation of our environmental variables (Supplementary Fig.~5). The comparison between the other parameter estimates revealed additional, somewhat more expected, relationships. In particular, we found the amplitude of distributions to be positively and negatively correlated with their mean and variance, respectively (i.e. $\alpha_{i}$ is positively correlated with $\beta_{i}$ and $\gamma_{i}$; Supplementary Fig.~XX). This implies that, at higher elevations, species' distributions generally have lower amplitudes.
